---
title: "Notes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(skimr)
library(ggplot2)
library(gapminder)
library(socviz)
p <- ggplot(data = gapminder)
p <- ggplot(data = gapminder,
            mapping = aes(x = gdpPercap, y = lifeExp))
p + geom_point()+
  geom_smooth(method = "gam") +
  scale_x_log10()
p + geom_smooth(method = lm) + geom_point()

```





```{r}
p <- ggplot(data = gapminder,
            mapping = aes(x = gdpPercap, y = lifeExp))
p +geom_point(color = "purple")+
  geom_smooth(method = "loess") +
  scale_x_log10()
```



```{r}
p + geom_point(alpha = 0.3) +
  geom_smooth(color = "red", se = FALSE, size = 8, method = "lm") +
  scale_x_log10()
```


```{r}
p <- ggplot(data = gapminder,
            mapping = aes(x = gdpPercap, y = lifeExp,
                          color = continent))
p +geom_point(color = "purple")+
  geom_smooth(method = "loess") +
  scale_x_log10()
```

```{r}
#saving work
ggsave()

# here() starts at the directory where the project is created
#create the figures folder in the directory where the project is created
```


```{r}
p <- ggplot(data = gapminder,
            mapping = aes(x = year,
                          y = gdpPercap))
p + geom_line()
```



```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = age, y = childs))

p + geom_point(alpha = 0.2) +
  geom_smooth() +
  facet_grid(sex ~ race)
```


```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion))
p + geom_bar()
```


```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion))
p + geom_bar(mapping = aes(y = ..prop..))
```


```{r}
table(gss_sm$religion)
```


```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = religion, color = religion))
p + geom_bar()
```


```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = religion, color = religion))
p + geom_bar() + guides()
```



```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion, fill = religion))
p + geom_bar()
```


```{r}
```p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion, fill = religion))
p + geom_bar(position = "fill")
```


```{r}
p <- ggplot(data = gss_sm,
            mapping = aes(x = bigregion, fill = religion))
p + geom_bar(position = "dodge",
             mapping = aes(y = ..prop.., roup = religion))
```


```{r}
p <- ggplot( data = midwest,
             mapping = aes(x = area))
p + geom_histogram
```
```{r}

oh_wi <- c("OH", "WI")

p <- ggplot(data = subset(midwest, subset = state %in% oh_wi),
            mapping = aes(x = percollege, fill = state))
p + geom_histogram(alpha = 0.4, bins = 20)
```



```{r}
p <- ggplot(data = ,idwest,
            mapping = aes(x = area))
p + geom_density()
```



```{r}
oh_wi <- c("OH", "WI")

p <- ggplot(data = subset(midwest, subset = state %in% oh_wi),
            mapping = aes(x = area, fill = state, color = state))
p + geom_density(alpha = 0.3, mapping = (aes(y = ..scaled..))
```


```{r}
p <- ggplot(data = titanic,
            mapping = aes(x = fate, y = percent, fill = sex))
p + geom_bar(position = "dodge", stat = "identity") + theme(legend.position = "top")
```


```{r}
p <- ggplot(data = oecd_sum,
            mapping = aes(x = year, y = diff, fill = hi_lo))
p + geom_col() + guides( fill = "none") +
  labs (x = NULL, y = "Difference in Years",
        title = "The US Life Expectancy Gap",
        subtitle = "Difference between US and OECD
        average life expectancies, 1960-2015",
        caption = "Data: OECD. After a chart by Christopher Ingraham, Wahsington Post, December 27th 2017,")
```


```{r}
